---
title: "Assignment 4"
author: "pushaan"
date: "3/7/2021"
output: html_document
---

# Question 1 parallel coordinate plot
```{r}

ny_accidents <- read.csv("C:/IE6600/ny_accidents.csv")

ny_accidents[ny_accidents==""] <- NA
ny_accidents<- ny_accidents[!is.na(ny_accidents$BOROUGH),]
library(hrbrthemes)
library(GGally)
library(ggplot2)
library(tidyr)
library(dplyr)

data <- ny_accidents

data <- data[,-(1:2),drop=FALSE]
data <- data[,-(2:10),drop=FALSE]
data <- data[,-(8:18),drop=FALSE]
data$num
data1<-data%>%
  group_by(BOROUGH)%>%
  summarise(pedestriansinjured=sum(NUMBER.OF.PEDESTRIANS.INJURED,na.rm = T),
            pedestrianskilled=sum(NUMBER.OF.PEDESTRIANS.KILLED,na.rm = T),
            cyclistinjured=sum(NUMBER.OF.CYCLIST.INJURED,na.rm = T),
            cyclistkilled=sum(NUMBER.OF.CYCLIST.KILLED,na.rm = T),
            motoristinjured=sum(NUMBER.OF.MOTORIST.INJURED,na.rm = T),
            motoristkilled=sum(NUMBER.OF.MOTORIST.KILLED,na.rm = T))

ggparcoord(data1, columns = 2:7  , groupColumn =1 ,
showPoints = TRUE,
title = "Parallel Coordinate Plot for NY Collisions",
scale="globalminmax")
```

#drawback of the parallel coordinate plot is scaling.I have changed the scaling from "globalminmax" to "std".I have also changed the font size since it was difficult to read.
```{r}
ggp1<- ggparcoord(data1, columns = 2:7  , groupColumn =1 ,
showPoints = TRUE,
title = "Parallel Coordinate Plot for NY Collisions",
scale="std")
ggp1 + theme(text = element_text(size = 8))

```

#Question 2 
```{r}
library(readxl)
library(GGally)
library(tidyr)
SAT <- read_excel("C:/IE6600/sat_performance (1).xlsx")
SAT<- na.omit(SAT)
#paired correlation
ggpairs(data = SAT, columns = c(4,5,6))

#box plot
SAT_pivot <- pivot_longer(data = SAT, cols = c(4,5,6), names_to = "topic",values_to = "Averagescore")
ggplot(SAT_pivot, aes(x=topic,y= Averagescore)) + geom_boxplot()

#density plot
ggplot(SAT_pivot, aes(x=Averagescore, fill=topic)) + geom_density(alpha=0.5)

```

#Question 3
```{r}
library(readxl)
library(GGally)
library(tidyr)
library(ggplot2)
library(plotly)
MHI <- read_excel("C:/IE6600/Question 3 dataset.xlsx")
colnames(MHI) <- c("Median_Income","District Name")
MHI_SAT<- merge(SAT,MHI, by ="District Name")
MHI_SAT$Average_score <- round((MHI_SAT$Reading+MHI_SAT$Writing+MHI_SAT$Math)/3)

plot <- ggplot(data = MHI_SAT, aes(x= Average_score,y=Median_Income, color=`District Name`))+geom_point(stat = "identity", show.legend = F)
ggplotly(plot)


```

#Observations on the question number 3
#1)As the Median_income increases the Average_score also increases
#2)Weston has the highest Median_income while Lexington has the highest Average_score.
#3)Springfield and Lawrence both have the lowest Median_income and also the lowest Average_score.